Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-05 WRITEUP/arxiv1/ms.tex
minor wording

% --------------------------------------------
\IfFileExists{emulateapjlegacy.cls}{\documentclass[iop]{emulateapjlegacy}}{\documentclass[iop]{emulateapj}}

\def\altomega{\varpi}
\usepackage{amsmath}

\input{preamble}
\slugcomment{To be Submitted.}

@@

\usepackage{xcolor}
\definecolor{apcolor}{HTML}{b3003b}
\definecolor{dlcolor}{HTML}{FF7F00}
\newcommand{\AP}[1]{({\bf \color{apcolor} AP: #1})}
\newcommand{\DL}[1]{({\bf \color{dlcolor} DL: #1})}
\definecolor{afcolor}{HTML}{b3443c}
\newcommand{\AF}[1]{({\bf \color{afcolor} AF: #1})}
\definecolor{mmcolor}{HTML}{006600}
\newcommand{\MM}[1]{({\bf \color{mmcolor} MM: #1})}

% it can be instead included as
% \graphicspath{{Fig/}}
% so that plots are automatically searched for in the given path
\def\figpath{./Fig}

@@

Based on Equation~\ref{eqn:SVE}, a one-to-one mapping between $\sigma_{\rm gas}^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, since $\sigma_{\rm gas}^2/R\propto\Sigma$.
%
\citep{Heyer09a} pointed out that the original size-linewidth relation implies constant surface density in this interpretation. The limited dynamic range in column density of CO observations appears to account for this \citep[see also][]{Ballesteros-Paredes11a}.
%
Deviations from this relation are often attributed to a significant contribution from external pressure as per Equation~\ref{eqn:v0} (see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}). Similar conclusions are also reached from the
analysis of clouds forming in a Milky-Way like galaxy simulated with a $\simeq 4\,{\rm pc}$ resolution \citep[i.e.][]{grisdale:2018}.

@@

% ------------------
\section{Numerical Simulations}\label{sec:sim}
The simulations used in this work are described by \citet{Pallottini17a, Pallottini17b} and are briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in Italian.} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$. The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, equivalent at initial density to a baryonic mass resolution of $1.2 \times 10^4 \Msun$. This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryonic) mass exceeds the mass resolution by a factor of eight. The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e. sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
%
The models include a non-equilibrium chemical network following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme described by \citet{Pallottini17a}.

@@

\begin{figure*}[hptb]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    {\it Top}: Star formation history of \flower. {\it Bottom}: projected stellar mass distribution during {\it (a)} an early accreting phase;
    %
    {\it (b)} a major starburst following a merger event; and {\it (c)} a relatively quiescent post-starburst phase.
    \label{fig:SFH}
   }
\end{figure*}

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
\caption{Normalized distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
    (a)}.
\label{fig:h2density}}
\end{figure}

\begin{figure*}[htbp]
 \centering
  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{\figpath/SS_bigfonts/{combined}.pdf}
\caption{
Examples of MCCs identified in \flower by our clump finder.
%
The identified structures (white contour) are superimposed on the map of the mass weighted $H_2$ density field of the galaxy.
%
Two stages of \flower are selected: the accreting phase (left two columns, see \Fig{SFH}a for the definition) and the quiescent phase (right two columns), where \flower display a highly disturbed gas morphology, and a rotating disk configuration, respectively.
%
Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles.
%
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$, as annotated in each panel.
\label{fig:MCC}
}
\end{figure*}

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The full velocity dispersion of MCCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
\begin{equation}
\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas. Therefore, when calculating global quantities for MCS, we always perform a mass-weighting. Since we operate on data on a uni-grid, this is equivalent to density averaged quantities. In general, for the quantity $x$ in a MCC we write
\begin{equation}\label{eqn:defineaverage}
\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells indexed by $i$ composing the MCC. We can use the definition \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
%
The bulk velocity dispersion is
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
\end{equation}
%
The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
\begin{equation}
c_s^2 = \left\langle \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right\rangle\,,
\end{equation}
where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton. Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
\begin{equation}
\sigma_{\rm NT}^2 = \left\langle \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n}\right\rangle\,.
\end{equation}
%
Finally, the Mach number is related to the pressure terms as follows
\begin{equation}
\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
\label{eqn:MPress}
\end{equation}

@@

\subsection{MCC Basic Properties} \label{sec:dist}
\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation. Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
\caption{Cloud mass and gas mass ratio of MCCs identified in the accreting phase of \flower using different $n_{\rm cut}$ (see colorbar). The most massive structures identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
%
Thus, these structures encompass a large amount of stellar mass that is already assembled in \flower. These disk/arm structures are excluded in the discussion of MCC dynamics in the remainder of this paper.
\label{fig:stellarRatio16}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-veldisp.pdf}
\caption{Gas velocity dispersions resulting from bulk versus turbulent motions for molecular structures
identified across all values of $n_{\rm cut}$, shown using the same color-coding as \Fig{stellarRatio16}.
%
Top and bottom panels show structures identified in the accreting phase and the quiescent phase, respectively.
The accreting phase of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (see \Fig{MCC}).
%
The dashed black lines show a one-to-one mapping between the axes to facilitate comparison.
%
Velocity dispersion from turbulent motions dominates over bulk motions for MCCs in the accreting phase, whereas
$\sigma_{\rm bulk}$ is comparable to $\sigma_{\rm NT}$ for some MCCs in the quiescent disk-like phase.
\label{fig:vv}}
\vspace{0.5em}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MCCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting (left) and starburst (right).
%
Star symbols are color-coded by density thresholds $n_{\rm cut}$, as illustrated by the colorbar shown on the right.
%
Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
%
The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for the gas to be in equilibrium, see Equation~\ref{eqn:v0}. Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a,
Swinbank11a, Leroy15a, Kauffmann17a}, and \citet{Kauffmann17b}. MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing molecular gas structures identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar on the right). Left panels show structures identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and the right panels show those identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
%
The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel).
%
Notably less MCCs in the right panels owing to the fact that only few MCCs with neighboring cells reaching high H$_2$ densities of $n_{\rm cut}\simeq$19\,\cc. The high velocity dispersion in \flower is largely driven by non-thermal pressure (see \Fig{vv}).
\label{fig:alpha16-28}}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_2by2_0_2.0}.pdf}
\caption{
Surface density maps of the gas (top left) and stellar (top right) components of \flower (accreting phase) and their radial velocity dispersion maps projected onto the $xy$-plane (bottom panels). Center of mass positions of MCCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols as an illustrative example.
\label{fig:sigma}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_1.2}.pdf}
\caption{
Toomre $Q$ maps derived from the central $R$\eq1.2\,kpc of \flower. Contribution from the gas ($Q_{\rm gas}$) and the stellar ($Q_\star$) components is shown in the left and middle panels, respectively. The effective two-component Toomre $Q_{\rm eff}$ parameter map is shown in the right panel.
%
All maps are projected onto the plane of the disk, and a gaussian smoothing of width 30\,pc has been applied to the maps.
%
Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols. Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
%
Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations in relatively evolved and enriched systems at high redshifts.
\label{fig:Qeff}}
\end{figure*}

@@

Excluding the main structure (disk of \flower) identified, the typical mass and size of MCC is $R\simeq\,50$\,pc and $M_{\rm gas}\simeq\,10^{6.5}$\,\Msun, respectively. Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}). That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc). On the other hand, the gas velocity dispersion
of $\sigma_{\rm gas}\simeq$\,20-10\,\kms is rather insensitive to the adopted density threshold.

@@

High pressure MCCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc. This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their central regions \citep{Downes98a, Sakamoto08a}. In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}). On the other hand, the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows. The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
%
The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}. This would imply column density is not a fundamental properties of molecular clouds and not all molecular clouds are virialized.

@@

This also implies that \obs with spatial resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies. Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. With the Next Generation VLA\footnote{\url{http://library.nrao.edu/public/memos/ngvla/NGVLA\_21.pdf}}, which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
% 0.005" highest freq
In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and depend on
the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.

>>>>

% --------------------------------------------
\documentclass[iop]{emulateapj}

\def\altomega{\varpi}
\usepackage{amsmath}
\usepackage{xcolor}

\input{preamble}
\slugcomment{Submitted to ApJ.}

@@

@@

Based on Equation~\ref{eqn:SVE}, a one-to-one mapping between $\sigma_{\rm gas}^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, since $\sigma_{\rm gas}^2/R\propto\Sigma$.
%
\citep{Heyer09a} pointed out that the original size-linewidth relation implies constant surface density in this interpretation. The limited dynamic range in column density of CO observations appears to account for this \citep[see also][]{Ballesteros-Paredes11a}.
%
Deviations from this relation are often attributed to a significant contribution from external pressure as per Equation~\ref{eqn:v0} (see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}). Similar conclusions are also reached from the
analysis of clouds forming in a Milky-Way like galaxy simulated with a $\simeq 4\,{\rm pc}$ resolution \citep[i.e.,][]{grisdale:2018}.

@@

% ------------------
\section{Numerical Simulations}\label{sec:sim}
The simulations used in this work are described by \citet{Pallottini17a, Pallottini17b} and are briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in Italian.} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$. The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, equivalent at initial density to a baryonic mass resolution of $1.2 \times 10^4 \Msun$. This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryonic) mass exceeds the mass resolution by a factor of eight. The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e., sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
%
The models include a non-equilibrium chemical network following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme described by \citet{Pallottini17a}.

@@

\begin{figure*}[hptb]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{sfh.pdf}
\caption{
    {\it Top}: Star formation history of \flower. {\it Bottom}: projected stellar mass distribution during {\it (a)} an early accreting phase;
    %
    {\it (b)} a major starburst following a merger event; and {\it (c)} a relatively quiescent post-starburst phase.
    \label{fig:SFH}
   }
\end{figure*}

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{hist_test_16.pdf}
\caption{Normalized distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
    (a)}.
\label{fig:h2density}}
\end{figure}

\begin{figure*}[htbp]
 \centering
  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{combined.pdf}
\caption{
Examples of MCCs identified in \flower by our clump finder.
%
The identified structures (white contour) are superimposed on the map of the mass weighted $H_2$ density field of the galaxy.
%
Two stages of \flower are selected: the accreting phase (left two columns, see \Fig{SFH}a for the definition) and the quiescent phase (right two columns), where \flower display a highly disturbed gas morphology, and a rotating disk configuration, respectively.
%
Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles.
%
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$, as annotated in each panel.
\label{fig:MCC}
}
\end{figure*}

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e., $R \equiv (3 V /4 \pi)^{1/3}$.
%
The full velocity dispersion of MCCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
\begin{equation}
\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas. Therefore, when calculating the global quantities of MCCs, we always perform a mass-weighting. Since we operate on data on a uni-grid, this is equivalent to density averaged quantities. In general, for the quantity $x$ in a MCC we write
\begin{equation}\label{eqn:defineaverage}
\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells indexed by $i$ composing the MCC. We can use the definition \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
%
The bulk velocity dispersion is
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
\end{equation}
%
The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
\begin{equation}
c_s^2 = \left\langle \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right\rangle\,,
\end{equation}
where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton. Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
\begin{equation}
\sigma_{\rm NT}^2 = \left\langle \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n}\right\rangle\,.
\end{equation}
%
Finally, the Mach number is related to the pressure terms as follows
\begin{equation}
\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
\label{eqn:MPress}
\end{equation}

@@

\subsection{MCC Basic Properties} \label{sec:dist}
\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{minmaxNcut_basicDistributions.pdf}
\caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation. Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{cloud-mass_fgas.pdf}
\caption{Cloud mass and gas mass ratio of MCCs identified in the accreting phase of \flower using different $n_{\rm cut}$ (see colorbar). The most massive structures identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
%
Thus, these structures encompass a large amount of stellar mass that is already assembled in \flower. These disk/arm structures are excluded in the discussion of MCC dynamics in the remainder of this paper.
\label{fig:stellarRatio16}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{ss16-28-veldisp.pdf}
\caption{Gas velocity dispersions resulting from bulk versus turbulent motions for molecular structures
identified across all values of $n_{\rm cut}$, shown using the same color-coding as \Fig{stellarRatio16}.
%
Top and bottom panels show structures identified in the accreting phase and the quiescent phase, respectively.
The accreting phase of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (see \Fig{MCC}).
%
The dashed black lines show a one-to-one mapping between the axes to facilitate comparison.
%
Velocity dispersion from turbulent motions dominates over bulk motions for MCCs in the accreting phase, whereas
$\sigma_{\rm bulk}$ is comparable to $\sigma_{\rm NT}$ for some MCCs in the quiescent disk-like phase.
\label{fig:vv}}
\vspace{0.5em}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MCCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting (left) and starburst (right).
%
Star symbols are color-coded by density thresholds $n_{\rm cut}$, as illustrated by the colorbar shown on the right.
%
Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
%
The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for the gas to be in equilibrium, see Equation~\ref{eqn:v0}. Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a,
Swinbank11a, Leroy15a, Kauffmann17a}, and \citet{Kauffmann17b}. MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing molecular gas structures identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar on the right). Left panels show structures identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and the right panels show those identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
%
The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel).
%
Notably less MCCs in the right panels owing to the fact that only few MCCs with neighboring cells reaching high H$_2$ densities of $n_{\rm cut}\simeq$19\,\cc. The high velocity dispersion in \flower is largely driven by non-thermal pressure (see \Fig{vv}).
\label{fig:alpha16-28}}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{{ss16_toomre_combined_2by2_0_2.0}.pdf}
\caption{
Surface density maps of the gas (top left) and stellar (top right) components of \flower (accreting phase) and their radial velocity dispersion maps projected onto the $xy$-plane (bottom panels). Center of mass positions of MCCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols as an illustrative example.
\label{fig:sigma}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{{ss16_toomre_combined_3by1_0_1.2}.pdf}
\caption{
Toomre $Q$ maps derived from the central $R$\eq1.2\,kpc of \flower. Contribution from the gas ($Q_{\rm gas}$) and the stellar ($Q_\star$) components is shown in the left and middle panels, respectively. The effective two-component Toomre $Q_{\rm eff}$ parameter map is shown in the right panel.
%
All maps are projected onto the plane of the disk, and a gaussian smoothing of width 30\,pc has been applied to the maps.
%
Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols. Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
%
Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations in relatively evolved and enriched systems at high redshifts.
\label{fig:Qeff}}
\end{figure*}

@@

Excluding the main structure (disk of \flower) identified, the typical mass and size of MCC is $M_{\rm gas}\simeq\,10^{6.5}$\,\Msun and $R\simeq\,50$\,pc, respectively. Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}). That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc). On the other hand, the gas velocity dispersion
of $\sigma_{\rm gas}\simeq$\,20-10\,\kms is rather insensitive to the adopted density threshold.

@@

High pressure MCCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc. This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their central regions \citep{Downes98a, Sakamoto08a}. In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}). On the other hand, the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows. The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.

The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}. This would imply column density is not a fundamental properties of molecular clouds and not all molecular clouds are virialized.

@@

This also implies that \obs with spatial resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies. Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the highest frequency bands. With the Next Generation VLA\footnote{\url{http://library.nrao.edu/public/memos/ngvla/NGVLA\_21.pdf}}, which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
% 0.005" highest freq
In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and depend on
the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
